CorReg: model-based pretreatment for regression with correlated variables. Application in steel industry

### 2014-04-01 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@475 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

 Where some try to reduce the dimension and then just hope to have small correlations in the remaining dimensions,  we propose to focus on the correlations, giving a model with orthogonal covariates and an explicit structure between covariates. In fact we search the greatest set of orthogonal covariates to keep the maximum information but with an orthogonality constraint. This can be viewed as a pretreatment on the dataset allowing to use then other dimension reduction tools without suffering from correlations. %We only consider strong correlations (i.e. : problematic ones) thus we keep most of the information contained in the dataset. 
 %We will in a second time be able to use the remaining part of the information (sequential approach).

>>>>

 Where some try to reduce the dimension and then have to suppose having no correlations between the remaining covariates,  we propose to focus on the correlations, giving a model with orthogonal covariates and an explicit structure between covariates. In fact we search the greatest set of orthogonal covariates to keep the maximum information but with an orthogonality constraint. This can be viewed as a pretreatment on the dataset allowing to use then other dimension reduction tools without suffering from correlations. %We only consider strong correlations (i.e. : problematic ones) thus we keep most of the information contained in the dataset. 
 %We will in a second time be able to use the remaining part of the information (sequential approach).
